analisis-preliminar

### 2021-04-16 production/analisis-preliminar.Rmd
Actualización html
Se agrega code_folding y tabla de contenidos

---
title: "analisis-preliminar"
author: "Kevin Carrasco"
date: "26-01-2021"
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "analisis-preliminar"
author: "Kevin Carrasco"
date: "26-01-2021"
output:
  html_document: 
    toc: yes
    toc_float: yes
    number_sections: true
    code_folding: "hide"
  pdf_document: default
---
